Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2020-12-03 main.tex
One more read-through before submission, made a few more small missed changes

    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of, typically one, algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}. Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}. However, as with Aggregator Oblivious Encryption, these works are relatively restricted in application due to the limited operations provided.

@@

    \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}. They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier. While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.

@@

\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
The recursive nature of the problem definition above complicates defining and proving of security requirements for the localization scenario. As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.

@@

\subsection{Participant Capabilities} \label{subsec:capabilities}
Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
\begin{LaTeXdescription}
    \item[Global navigator broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required. We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.

    A problem caused by this requirement is apparent in the context of aircraft navigation. It may be the case that some sensors are not within the range of a navigator broadcast. We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party. An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localization instances with global broadcasts.
    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors. This means the navigator may not send different information to individual sensors during a single time-step.

    In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.

    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}. As privacy-preserving implementations of such mechanisms require additional complications, we will not consider the scenario in this work.
    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents. We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
\end{LaTeXdescription}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize]
    % Sizes
    \tikzmath{\srange = 3.54; \sradius = 0.04;}
    % Sensor locations (sensor 3 is shared)
    \coordinate (s1) at (0.8523,-4.1508) {};
    \coordinate (s2) at (3.507,-5.5587) {};
    \coordinate (s3) at (2.5,-2.75) {} {};
    \coordinate (s4) at (4,-1.25) {};
    \coordinate (s5) at (5.4346,-3.1274) {};
    % Navigator location
    \coordinate (nav_loc) at (3.5,-3.25) {};
    % Bounding rectangle
    \coordinate (brect_start) at (0,0);
    \coordinate (brect_end) at (6.5, -6.5);

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N} \\
    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

\begin{remark} \label{rem:lcao_leakage}
    The notion of an aggregator leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the navigator (in our case the aggregator), they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{remark}

@@

Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements. We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes. The considered layouts have been plotted and named in Figure~\ref{fig:sim_layouts}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layouts.pdf}
\caption{The considered layouts, with varying average distances between navigator and sensors.}
\label{fig:sim_layouts}
\end{figure}
To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances set to $r_i=5$ simulation distance units. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layout_errors.pdf}
\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
\label{fig:sim_layout_errors}
\end{figure}
From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter. The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.

>>>>

    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of (typically one) algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}. Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}. However, as with Aggregator Oblivious Encryption, these works are relatively restricted in application due to the limited operations provided.

@@

    \item[Multi-Client Functional Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}. They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier. While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.

@@

\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario. As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.

@@

\subsection{Participant Capabilities} \label{subsec:capabilities}
Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
\begin{LaTeXdescription}
    \item[Global Navigator Broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required. We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.

    A problem caused by this requirement is apparent in the context of aircraft navigation. It may be the case that some sensors are not within the range of a navigator broadcast. We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party. An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localization instances with global broadcasts.
    \item[Consistent Navigator Broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors. This means the navigator may not send different information to individual sensors during a single time-step.

    In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.

    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}. As privacy-preserving implementations of such mechanisms require additional complications, we will not consider the scenario in this work.
    \item[Computational Capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents. We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
\end{LaTeXdescription}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}[font=\footnotesize]
    % Sizes
    \tikzmath{\srange = 3.54; \sradius = 0.04;}
    % Sensor locations (sensor 3 is shared)
    \coordinate (s1) at (0.8523,-4.1508) {};
    \coordinate (s2) at (3.507,-5.5587) {};
    \coordinate (s3) at (2.5,-2.75) {} {};
    \coordinate (s4) at (4,-1.25) {};
    \coordinate (s5) at (5.4346,-3.1274) {};
    % Navigator location
    \coordinate (nav_loc) at (3.5,-3.25) {};
    % Bounding rectangle
    \coordinate (brect_start) at (0,0);
    \coordinate (brect_end) at (6.5, -6.5);

@@

In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
\begin{align}
    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
\end{align}

@@

\begin{remark} \label{rem:lcao_leakage}
    The notion of an aggregator leakage function including parameters from the aggregator requires extra care to be taken when giving its definition. Since an attacker may compromise the navigator (in our case the aggregator), they have control over the choice of these parameters, and therefore over the leakage function. We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
\end{remark}

@@

Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements. We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes. The considered layouts have been plotted and named in Figure~\ref{fig:sim_layouts}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layouts.pdf}
\caption{The considered layouts, with varying average distances between navigator and sensors.}
\label{fig:sim_layouts}
\end{figure}
To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units. Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF. The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
\begin{figure}[htbp]
\centering
\includegraphics{images/layout_errors.pdf}
\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
\label{fig:sim_layout_errors}
\end{figure}
From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter. The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.
